---
title: "caretcompaR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{caretcompaR}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---



An R package facilitating beautifully efficient comparisons of machine learning classifiers and models.

caretcompaR harnesses the power of caret, combining it with R dataframes for easy, breezy, and beautiful machine learning regressors and classifiers exploration.

Example Usage : 


```{r}



index <- caret::createDataPartition(iris$Species,p = 0.75,list=FALSE)
train_iris <- iris[index,]
test_iris <- iris[-index,]
X_train <-train_iris[,names(iris)!='Species'] 
y_train <- train_iris[,names(iris)=='Species'] 
X_test <- test_iris[,names(iris)!='Species'] 
y_test <- test_iris[,names(iris)=='Species'] 

models <- c('svmPoly','knn','rf')

print(models)

results_df <- caretcompaR::train_test_acc_time(models,X_train,y_train,X_test,y_test)

# Outputs the dataframe of performance of different models

results_df

# Plot the accuracy of the models 
caretcompaR::comparison_viz(results_df,'accuracy')


```




Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))